### 2018-01-10 ident/docs/ident_manuscript.tex
add new figure for experiments in k1cat identification

In the small model that we use to elucidate our methodology, we find that only 
\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.3\textheight]{C:/Users/shyam/Documents/Courses/CHE1125Project/Results/ident/figure1/noise_no_noise_kotte_ident_jan01}}
	\caption{The number of data sets, made from a combination of 18 different in silico experiments that can practically identify each parameter in fluxes a) $v_1$, b) $v_2$ and c) $v_3$ when there is no noise in the input experimental data. In the presence of additive noise in the flux and concentration data used for identifiability, the number of data sets practically identifying parameters in fluxes d) $v_1$, e) $v_2$ and f) $v_3$ are shown. 25 samples of additive noise $\epsilon ~ N(0, 0.05)$ were used to generate noisy data for figures in the right hand side panel.}\label{fig:figure1}
\end{figure}

>>>>

In the small model that we use to elucidate our methodology, we find that only 
\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.3\textheight]{C:/Users/shyam/Documents/Courses/CHE1125Project/Results/ident/figure1/noise_no_noise_kotte_ident_jan01}}
	\caption{The number of data sets, made from a combination of 18 different in silico experiments that can practically identify each parameter in fluxes a) $v_1$, b) $v_2$ and c) $v_3$ when there is no noise in the input experimental data. In the presence of additive noise in the flux and concentration data used for identifiability, the number of data sets practically identifying parameters in fluxes d) $v_1$, e) $v_2$ and f) $v_3$ are shown. 25 samples of additive noise $\epsilon ~ N(0, 0.05)$ were used to generate noisy data for figures in the right hand side panel.}\label{fig:figure1}
\end{figure}
\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.3\textheight]{C:/Users/shyam/Documents/Courses/CHE1125Project/Results/ident/figure2/k1cat_no_noise_experiments_jan03}}
	\caption{The contribution of different experiments types used in combinations that can practically identify parameter $k_1^{cat}$ in $v_1$. Panels a) and b) represent the position of the experiment in $k = \{1, 2\}$}\label{fig:figure2}
\end{figure}
